NumPy---Array Programming in Python

### 2020-02-05 body.tex
Minor edits

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
\emph{Application Programming Interface} (API) has become widespread as
a language for array programming.
To exploit new specialized hardware and storage, there has been
a recent proliferation of Python array packages.
Instead of leading back to some kind of Numarray and Numeric divide that
NumPy was created to bridge, NumPy has become ...

>>>>

Fifteen years later, NumPy now underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
\emph{Application Programming Interface} (API) has become widespread as
a language for array programming.
To exploit new specialized hardware and storage, there has been
a recent proliferation of Python array packages.
Instead of leading back to some kind of Numarray and Numeric divide that
NumPy was created to bridge, NumPy has become ...
